\Large \bf Redstone: a Modular Deterministic Simulation Testing Framework for Distributed Systems

### 2024-06-07 paper/paper.tex
Abstract done

% make title bold and 14 pt font (Latex default is non-bold, 16 pt)
\title{\Large \bf Redstone: a Deterministic Simulation Testing Framework for Distributed Systems}

@@

%-------------------------------------------------------------------------------
\begin{abstract}
%-------------------------------------------------------------------------------
Your abstract text goes here. Just a few facts. Whet our appetites.
Not more than 200 words, if possible, and preferably closer to 150.
\end{abstract}

@@

%-------------------------------------------------------------------------------
\section{Footnotes, Verbatim, and Citations}
%-------------------------------------------------------------------------------

Footnotes should be places after punctuation characters, without any
spaces between said characters and footnotes, like so.%
\footnote{Remember that USENIX format stopped using endnotes and is
now using regular footnotes.} And some embedded literal code may
look as follows.

\begin{verbatim}
int main(int argc, char *argv[]) 
{
return 0;
}
\end{verbatim}

Now we're going to cite somebody. Watch for the cite tag. Here it
comes. Arpachi-Dusseau and Arpachi-Dusseau co-authored an excellent OS
book, which is also really funny~\cite{arpachiDusseau18:osbook}, and
Waldspurger got into the SIGOPS hall-of-fame due to his seminal paper
about resource management in the ESX hypervisor~\cite{waldspurger02}.

The tilde character (\~{}) in the tex source means a non-breaking
space. This way, your reference will always be attached to the word
that preceded it, instead of going to the next line.

And the 'cite' package sorts your citations by their numerical order
of the corresponding references at the end of the paper, ridding you
from the need to notice that, e.g, ``Waldspurger'' appears after
``Arpachi-Dusseau'' when sorting references
alphabetically~\cite{waldspurger02,arpachiDusseau18:osbook}.

It'd be nice and thoughtful of you to include a suitable link in each
and every bibtex entry that you use in your submission, to allow
reviewers (and other readers) to easily get to the cited work, as is
done in all entries found in the References section of this document.

Now we're going take a look at Section~\ref{sec:figs}, but not before
observing that refs to sections and citations and such are colored and
clickable in the PDF because of the packages we've included.

%-------------------------------------------------------------------------------
\section{Floating Figures and Lists}
\label{sec:figs}
%-------------------------------------------------------------------------------

%---------------------------
\begin{figure}
\begin{center}
\begin{tikzpicture}
\draw[thin,gray!40] (-2,-2) grid (2,2);
\draw[<->] (-2,0)--(2,0) node[right]{$x$};
\draw[<->] (0,-2)--(0,2) node[above]{$y$};
\draw[line width=2pt,blue,-stealth](0,0)--(1,1)
node[anchor=south west]{$\boldsymbol{u}$};
\draw[line width=2pt,red,-stealth](0,0)--(-1,-1)
node[anchor=north east]{$\boldsymbol{-u}$};
\end{tikzpicture}
\end{center}
\caption{\label{fig:vectors} Text size inside figure should be as big as
caption's text. Text size inside figure should be as big as
caption's text. Text size inside figure should be as big as
caption's text. Text size inside figure should be as big as
caption's text. Text size inside figure should be as big as
caption's text. }
\end{figure}
%% %---------------------------

Here's a typical reference to a floating figure:
Figure~\ref{fig:vectors}. Floats should usually be placed where latex
wants then. Figure\ref{fig:vectors} is centered, and has a caption
that instructs you to make sure that the size of the text within the
figures that you use is as big as (or bigger than) the size of the
text in the caption of the figures. Please do. Really.

In our case, we've explicitly drawn the figure inlined in latex, to
allow this tex file to cleanly compile. But usually, your figures will
reside in some file.pdf, and you'd include them in your document
with, say, \textbackslash{}includegraphics.

Lists are sometimes quite handy. If you want to itemize things, feel
free:

\begin{description}

\item[fread] a function that reads from a \texttt{stream} into the
array \texttt{ptr} at most \texttt{nobj} objects of size
\texttt{size}, returning returns the number of objects read.

\item[Fred] a person's name, e.g., there once was a dude named Fred
who separated usenix.sty from this file to allow for easy
inclusion.
\end{description}

\noindent
The noindent at the start of this paragraph in its tex version makes
it clear that it's a continuation of the preceding paragraph, as
opposed to a new paragraph in its own right.

\subsection{LaTeX-ing Your TeX File}
%-----------------------------------

People often use \texttt{pdflatex} these days for creating pdf-s from
tex files via the shell. And \texttt{bibtex}, of course. Works for us.

>>>>

% make title bold and 14 pt font (Latex default is non-bold, 16 pt)
\title{\Large \bf Redstone: a Modular Deterministic Simulation Testing Framework for Distributed Systems}

@@

%-------------------------------------------------------------------------------
\begin{abstract}
%-------------------------------------------------------------------------------
In testing distributed systems,
confirming a system's tolerance of faults in disks and networks is not only useful but necessary.
Redstone, a modular deterministic simulation testing framework,
amplifies failures in various substrates underlying a distributed system
in order to confirm the system's ability to withstand these failures.
We intercept calls to the kernel for the disk and the network, as well as to clock functions,
introducing our own code.
Determinism allows reproduction of failure conditions,
allowing developers to confirm, having encountered and debugged a failure,
that their system will not fail again when confronted by identical conditions.
Our control over clock functions further allows us to "accelerate" time,
increasing ability to test faster, and to emulate the effects of clock jitter.
Finally, because Redstone is inherently modular,
it is simple to extend and port to a wider variety of applications and platforms.
\end{abstract}

@@

% %-------------------------------------------------------------------------------
% \section{Footnotes, Verbatim, and Citations}
% %-------------------------------------------------------------------------------
% 
% Footnotes should be places after punctuation characters, without any
% spaces between said characters and footnotes, like so.%
% \footnote{Remember that USENIX format stopped using endnotes and is
% now using regular footnotes.} And some embedded literal code may
% look as follows.
% 
% \begin{verbatim}
% int main(int argc, char *argv[]) 
% {
% return 0;
% }
% \end{verbatim}
% 
% Now we're going to cite somebody. Watch for the cite tag. Here it
% comes. Arpachi-Dusseau and Arpachi-Dusseau co-authored an excellent OS
% book, which is also really funny~\cite{arpachiDusseau18:osbook}, and
% Waldspurger got into the SIGOPS hall-of-fame due to his seminal paper
% about resource management in the ESX hypervisor~\cite{waldspurger02}.
% 
% The tilde character (\~{}) in the tex source means a non-breaking
% space. This way, your reference will always be attached to the word
% that preceded it, instead of going to the next line.
% 
% And the 'cite' package sorts your citations by their numerical order
% of the corresponding references at the end of the paper, ridding you
% from the need to notice that, e.g, ``Waldspurger'' appears after
% ``Arpachi-Dusseau'' when sorting references
% alphabetically~\cite{waldspurger02,arpachiDusseau18:osbook}. 
% 
% It'd be nice and thoughtful of you to include a suitable link in each
% and every bibtex entry that you use in your submission, to allow
% reviewers (and other readers) to easily get to the cited work, as is
% done in all entries found in the References section of this document.
% 
% Now we're going take a look at Section~\ref{sec:figs}, but not before
% observing that refs to sections and citations and such are colored and
% clickable in the PDF because of the packages we've included.
% 
% %-------------------------------------------------------------------------------
% \section{Floating Figures and Lists}
% \label{sec:figs}
% %-------------------------------------------------------------------------------

% %---------------------------
% \begin{figure}
% \begin{center}
% \begin{tikzpicture}
% \draw[thin,gray!40] (-2,-2) grid (2,2);
% \draw[<->] (-2,0)--(2,0) node[right]{$x$};
% \draw[<->] (0,-2)--(0,2) node[above]{$y$};
% \draw[line width=2pt,blue,-stealth](0,0)--(1,1)
% node[anchor=south west]{$\boldsymbol{u}$};
% \draw[line width=2pt,red,-stealth](0,0)--(-1,-1)
% node[anchor=north east]{$\boldsymbol{-u}$};
% \end{tikzpicture}
% \end{center}
% \caption{\label{fig:vectors} Text size inside figure should be as big as
% caption's text. Text size inside figure should be as big as
% caption's text. Text size inside figure should be as big as
% caption's text. Text size inside figure should be as big as
% caption's text. Text size inside figure should be as big as
% caption's text. }
% \end{figure}
% %% %---------------------------

% Here's a typical reference to a floating figure:
% Figure~\ref{fig:vectors}. Floats should usually be placed where latex
% wants then. Figure\ref{fig:vectors} is centered, and has a caption
% that instructs you to make sure that the size of the text within the
% figures that you use is as big as (or bigger than) the size of the
% text in the caption of the figures. Please do. Really.
% 
% In our case, we've explicitly drawn the figure inlined in latex, to
% allow this tex file to cleanly compile. But usually, your figures will
% reside in some file.pdf, and you'd include them in your document
% with, say, \textbackslash{}includegraphics.
% 
% Lists are sometimes quite handy. If you want to itemize things, feel
% free:
% 
% \begin{description}
% 
% \item[fread] a function that reads from a \texttt{stream} into the
% array \texttt{ptr} at most \texttt{nobj} objects of size
% \texttt{size}, returning returns the number of objects read.
% 
% \item[Fred] a person's name, e.g., there once was a dude named Fred
% who separated usenix.sty from this file to allow for easy
% inclusion.
% \end{description}
% 
% \noindent
% The noindent at the start of this paragraph in its tex version makes
% it clear that it's a continuation of the preceding paragraph, as
% opposed to a new paragraph in its own right.
% 
% 
% \subsection{LaTeX-ing Your TeX File}
% %-----------------------------------
% 
% People often use \texttt{pdflatex} these days for creating pdf-s from
% tex files via the shell. And \texttt{bibtex}, of course. Works for us.
